Case Study: ChIP-seq Differential Peak Calling (pre-defined regions)

### 2018-08-23 datasets/ChIP-seq/ChIPseq-h3k4me3-promoters.Rmd
Fix typo in ChIPseq; adjust pvalue histograms

We test for differential peaks at each of the .

@@

```{r, chipseq-diag-hist, fig.width=10, fig.height=3.2}
strat_hist(dat, pvalue = "pval", covariate = "ind_covariate",
           maxy = 10)
```

>>>>

We test for differential binding at each of the promoters.

@@

```{r, chipseq-diag-hist, fig.width=10, fig.height=3.2}
strat_hist(dat, pvalue = "pval", covariate = "ind_covariate",
           maxy = 30)
```
